
---
title: "Size of impulses and corrections"
output: html_document
---

<style>
.main-container {
    max-width: 940px;
    margin-left: 0;
    margin-right: auto;
}
</style>


Version: 1.0

```{r, echo=FALSE, message=FALSE,warning=FALSE}
##This code takes files from the optimoraR optimization and rank them by best results.

library(dplyr)
library(ggplot2)
library(plotly)
library(Stocks)
library(data.table)
library(hexbin)
library(splitstackshape)
 library(zoo)
library(tidyr)
library(knitr)
library(ggpubr)
library(dygraphs)

PerCorrection= c(0.1, 0.15, 0.2, 0.25, 0.5)
CriticalSwing=3 # percent change used to identify critical extensions

#Plots for corrections
Data=read.csv("D:/Scrips/Trading/ForexPairs2YrsAll.csv")

Data=cbind(ID=1:nrow(Data),Data)

Data=Data %>% filter(TF =="1 min")



TickersOpt=sort(unique(Data$TickerNam))

Results=data.frame()

for (TickerI in TickersOpt){
  DataTickerI=Data %>% filter(TickerNam ==TickerI)

  
  for (CorrectionI in PerCorrection){
    #Frequency of swing sizes
  SizeSwins=ZigZag_Frequency.Swings(DataTickerI$c,change=CorrectionI)
    Feq2=data.frame(Impulse =lag(SizeSwins),Correction=SizeSwins)
    Feq2=Feq2 %>% filter(Impulse  >=0)
    Feq2$MinCorrection=CorrectionI
    Feq2$TickerNam=TickerI
    Results=rbind(Results,Feq2)
  }
  
}


#do zizag frequency hexbin density plots
for (Ticker in TickersOpt){

StockIData=Results %>% filter(TickerNam ==Ticker)

xLim=range(StockIData$Impulse)
yLim=range(StockIData$Correction)

for (I in 1:length(PerCorrection)){
  GGPLOT=ggplot((StockIData %>% filter(MinCorrection  ==PerCorrection[I])), aes(x = Impulse , y = Correction )) + geom_hex(show.legend=FALSE ) +  xlim(xLim) + ylim(yLim)+labs(x=PerCorrection[I]) +
    theme(axis.title.x = element_text(vjust = 2)) + geom_hline(yintercept=-CriticalSwing, linetype="dashed", color = "red",size=0.5)+ geom_vline(xintercept=CriticalSwing, linetype="dashed", color = "red",size=0.5)
  Name=paste0(Ticker,"_",I)
  assign(Name,ggplotly(GGPLOT))
}
}




    
```



These plots show the mimimum price correction at given price extensions... this is like the zig-zag indicator in trdingview, ploting the increases and decreases of certain sizes.

$$\\[.0005in]$$





# AUDUSD


```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(AUDUSD_1,AUDUSD_2,AUDUSD_3,AUDUSD_4,AUDUSD_5,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    





# EURAUD 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(EURAUD_1,EURAUD_2,EURAUD_3,EURAUD_4,EURAUD_5,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# EURCAD 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(EURCAD_1,EURCAD_2,EURCAD_3,EURCAD_4,EURCAD_5,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# EURCHF 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(EURCHF_1,EURCHF_2,EURCHF_3,EURCHF_4,EURCHF_5,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# EURGBP 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(EURGBP_1,EURGBP_2,EURGBP_3,EURGBP_4,EURGBP_5,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# EURJPY 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(EURJPY_1,EURJPY_2,EURJPY_3,EURJPY_4,EURJPY_5,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# EURNZD 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(EURNZD_1,EURNZD_2,EURNZD_3,EURNZD_4,EURNZD_5,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# EURUSD 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(EURUSD_1,EURUSD_2,EURUSD_3,EURUSD_4,EURUSD_5,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# GBPAUD 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(GBPAUD_1,GBPAUD_2,GBPAUD_3,GBPAUD_4,GBPAUD_5,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# GBPCAD 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(GBPCAD_1,GBPCAD_2,GBPCAD_3,GBPCAD_4,GBPCAD_5,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```


$$\\[.0009in]$$    


# GBPCHF 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(GBPCHF_1,GBPCHF_2,GBPCHF_3,GBPCHF_4,GBPCHF_5,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# GBPJPY 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(GBPJPY_1,GBPJPY_2,GBPJPY_3,GBPJPY_4,GBPJPY_5,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# GBPNZD 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(GBPNZD_1,GBPNZD_2,GBPNZD_3,GBPNZD_4,GBPNZD_5,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# GBPUSD 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(GBPUSD_1,GBPUSD_2,GBPUSD_3,GBPUSD_4,GBPUSD_5,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# NZDUSD 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(NZDUSD_1,NZDUSD_2,NZDUSD_3,NZDUSD_4,NZDUSD_5,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# USDCAD 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(USDCAD_1,USDCAD_2,USDCAD_3,USDCAD_4,USDCAD_5,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# USDCHF 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(USDCHF_1,USDCHF_2,USDCHF_3,USDCHF_4,USDCHF_5,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# USDJPY 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(USDJPY_1,USDJPY_2,USDJPY_3,USDJPY_4,USDJPY_5,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# XAUUSD

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(XAUUSD_1,XAUUSD_2,XAUUSD_3,XAUUSD_4,XAUUSD_5,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    

