
---
title: "Ranking of optimized robots"
output: html_document
---

Version: 1.0

```{r, echo=FALSE, message=FALSE,warning=FALSE}
##This code takes files from the optimoraR optimization and rank them by best results.

library(dplyr)
library(ggplot2)
library(plotly)
library(Stocks)
library(data.table)

library(splitstackshape)
#
library(tidyr)
library(knitr)
library(ggpubr)
PerCorrection=0.15

FilePath=dirname(rstudioapi::getSourceEditorContext()$path)
FilesPriorBot=  data.frame(FileName=list.files(paste0(FilePath,"/")))
FilesPriorBot=data.frame(FileName=FilesPriorBot[grep("csv", x = FilesPriorBot$FileName),])


Optimizations=data.frame()
for (FileIinBot in FilesPriorBot$FileName){
  OptimizationName=FileIinBot
  BotName=sub(".csv", "", FileIinBot)
  ResultOptimizationI= read.csv(paste0(FilePath,"/",FileIinBot)) 
  ResultOptimizationI$BotName=BotName
  Optimizations=rbind(Optimizations,ResultOptimizationI)
}

Optimizations$X=NULL
Optimizations=Optimizations %>%  filter(ProfitPerDay  > 0)

#Max per day
Max= Optimizations %>% group_by(Ticker) %>% summarize(Max = max(ProfitPerDay ))
DailyYield=round(sum(Max$Max),1)
DailyYieldAsPercent=round((DailyYield*100)/30000, 2)
Pairs=unique(Optimizations$Ticker)

for (TickerI in Pairs){
    DataTickerI=Optimizations %>% filter(Ticker ==TickerI)
    DataTickerI=DataTickerI[order(DataTickerI$ProfitPerDay , decreasing = TRUE), ] 
    Rank=1:nrow(DataTickerI)
    DataTickerI=cbind(Rank,DataTickerI)
    DataTickerI=DataTickerI %>% mutate_if(is.numeric, round, digits=0)
    DataTickerI$ParNames=gsub("/", "<br>", DataTickerI$ParNames)
    DataTickerI$ParValues=gsub("/", "<br>", DataTickerI$ParValues)
    #do bar plot
Opti=ggplot(DataTickerI, aes(x=Rank, y=ProfitPerDay ,  fill = BotName)) +
     geom_col(position = position_dodge())+
     geom_hline(yintercept=100, linetype="dashed", color = "red",size=0.5)+
     theme_gray()+ 
     theme(legend.title = element_blank())

   assign(TickerI,ggplotly(Opti, tooltip ="Rank"))
  TableName=paste0("Data_", TickerI)
    assign(TableName,DataTickerI)
}

#Plots for corrections
Data=read.csv("D:/Scrips/Trading/ForexPairs2Yrs.csv")
Data=cbind(ID=1:nrow(Data),Data)

Data=Data %>% filter(TF =="1 min")



TickersOpt=unique(Data$TickerNam)

for (TickerI in TickersOpt){
  DataTickerI=Data %>% filter(TickerNam ==TickerI)
  
  Freq.2=ZigZag_Frequency.Swings(DataTickerI$c,change=PerCorrection)
  Feq2=data.frame(Impulse =lag(Freq.2),Correction=Freq.2)
  Feq2=Feq2 %>% filter(Impulse  >=0)

  HexName=paste0("Hex_", TickerI)
  GGPLOT=ggplot(Feq2, aes(x = Impulse , y = Correction )) + geom_hex(show.legend=FALSE ) 
  assign(HexName,ggplotly(GGPLOT))
}

    
```

$$\\[.0005in]$$
 <font size="25"> **$ `r DailyYield` per day** </font>   <font size="3">  (`r DailyYieldAsPercent` percent per day) </font>  
 



$$\\[.0005in]$$

Bots are optimized by having the largest number of successful entries while meeting as criteria that DD does not exceed the desired DD (%20) and the entry capital not larger than 10% nor smaller than $1,000 (The smallest amount possible).


Optimized with $30,000 capital, 10% of capital per entry and 20% desired DD.

Density plots show for maximum price impulse (Price increase or decreases) for a correction larger than `r PerCorrection` percent. In other words, what has been the maximum price decline in the last 2 years for an expected correction of `r PerCorrection` percent.

$$\\[.0005in]$$




# AUDUSD


```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =10}
subplot(Hex_AUDUSD,AUDUSD, titleY = TRUE,   titleX = TRUE, margin = 0.05, which_layout=2)

```

    
  

<details>
  <summary>Parameters</summary>
```{r, echo=FALSE, eval=TRUE}

knitr::kable(Data_AUDUSD)
```
</details> 



$$\\[.0005in]$$


# EURGBP



```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =10}
subplot(Hex_EURGBP,EURGBP, titleY = TRUE, titleX = TRUE, margin = 0.05, which_layout=2)

```

    
  

<details>
  <summary>Parameters</summary>
```{r, echo=FALSE, eval=TRUE}

knitr::kable(Data_EURGBP)
```
</details> 

   
$$\\[.0005in]$$    


# EURJPY



```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =10}
subplot(Hex_EURJPY,EURJPY, titleY = TRUE, titleX = TRUE, margin = 0.05, which_layout=2)

```

    
  

<details>
  <summary>Parameters</summary>
```{r, echo=FALSE, eval=TRUE}

knitr::kable(Data_EURJPY)
```
</details> 

    
    
   
$$\\[.0005in]$$




# EURUSD



```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =10}
subplot(Hex_EURUSD,EURUSD, titleY = TRUE, titleX = TRUE, margin = 0.05, which_layout=2)

```

    
  

<details>
  <summary>Parameters</summary>
```{r, echo=FALSE, eval=TRUE}

knitr::kable(Data_EURUSD)
```
</details> 



   
$$\\[.0005in]$$


# GBPJPY



```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =10}
subplot(Hex_GBPJPY,GBPJPY, titleY = TRUE, titleX = TRUE, margin = 0.05, which_layout=2)

```

    
  

<details>
  <summary>Parameters</summary>
```{r, echo=FALSE, eval=TRUE}

knitr::kable(Data_GBPJPY)
```
</details> 


   
$$\\[.0005in]$$



# GBPUSD



```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =10}
subplot( Hex_GBPUSD,GBPUSD,titleY = TRUE, titleX = TRUE, margin = 0.05, which_layout=2)

```

    
  

<details>
  <summary>Parameters</summary>
```{r, echo=FALSE, eval=TRUE}

knitr::kable(Data_GBPUSD)
```
</details> 


   
$$\\[.0005in]$$



# NZDUSD



```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center' , fig.width =10}
subplot(Hex_NZDUSD,NZDUSD, titleY = TRUE, titleX = TRUE, margin = 0.05, which_layout=2)

```

    
  

<details>
  <summary>Parameters</summary>
```{r, echo=FALSE, eval=TRUE}

knitr::kable(Data_NZDUSD)
```
</details> 


   
$$\\[.0005in]$$



# USDCAD



```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =10}
subplot(Hex_USDCAD,USDCAD, titleY = TRUE, titleX = TRUE, margin = 0.05, which_layout=2)

```

    
  

<details>
  <summary>Parameters</summary>
```{r, echo=FALSE, eval=TRUE}

knitr::kable(Data_USDCAD)
```
</details> 


   
$$\\[.0005in]$$


# USDCHF



```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =10}
subplot(Hex_USDCHF,USDCHF, titleY = TRUE, titleX = TRUE, margin = 0.05, which_layout=2)

```

    
  

<details>
  <summary>Parameters</summary>
```{r, echo=FALSE, eval=TRUE}

knitr::kable(Data_USDCHF)
```
</details> 



   
$$\\[.0005in]$$



# USDJPY



```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =10}
subplot(Hex_USDJPY,USDJPY, titleY = TRUE, titleX = TRUE, margin = 0.05, which_layout=2)

```

    
  

<details>
  <summary>Parameters</summary>
```{r, echo=FALSE, eval=TRUE}

knitr::kable(Data_USDJPY)
```
</details> 


   
$$\\[.0005in]$$


# XAUUSD



```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =10}
subplot( Hex_XAUUSD,XAUUSD,titleY = TRUE, titleX = TRUE, margin = 0.05,  which_layout=2)

```

    
  

<details>
  <summary>Parameters</summary>
```{r, echo=FALSE, eval=TRUE}

knitr::kable(Data_XAUUSD)
```
</details> 
