
---
title: "Size of impulses and corrections"
output: html_document
---

<style>
.main-container {
    max-width: 940px;
    margin-left: 0;
    margin-right: auto;
}
</style>


Version: 1.0

```{r, echo=FALSE, message=FALSE,warning=FALSE}
##This code takes files from the optimoraR optimization and rank them by best results.

library(dplyr)
library(ggplot2)
library(plotly)
library(Stocks)
library(data.table)
library(hexbin)
library(splitstackshape)
 library(zoo)
library(tidyr)
library(knitr)
library(ggpubr)
library(dygraphs)

PerCorrection= c(0.05, 0.1, 0.15, 0.2, 0.25, 0.5)
CriticalSwing=2 # percent change used to identify critical extensions

#Plots for corrections
Data=read.csv("D:/Scrips/Trading/ForexPairs2YrsAll.csv")

Data=cbind(ID=1:nrow(Data),Data)

Data=Data %>% filter(TF =="1 min")



TickersOpt=sort(unique(Data$TickerNam))

Results=data.frame()

for (TickerI in TickersOpt){
  DataTickerI=Data %>% filter(TickerNam ==TickerI)

  
  for (CorrectionI in PerCorrection){
    #Frequency of swing sizes
  SizeSwins=ZigZag_Frequency.Swings(DataTickerI$c,change=CorrectionI)
    Feq2=data.frame(Impulse =lag(SizeSwins),Correction=SizeSwins)
    Feq2=Feq2 %>% filter(Impulse  >=0)
    Feq2$MinCorrection=CorrectionI
    Feq2$TickerNam=TickerI
    Results=rbind(Results,Feq2)
  }
  
}


#do zizag frequency hexbin density plots
for (Ticker in TickersOpt){

StockIData=Results %>% filter(TickerNam ==Ticker)


xLim=max(StockIData$Impulse)
yLim=min(StockIData$Correction)

if( xLim > CriticalSwing) {xLim= c(0, xLim +0.5)} else {xLim= c(0, CriticalSwing +0.5)}
if( yLim < -CriticalSwing) {yLim= c( yLim -0.5, 0)} else {yLim= c( -CriticalSwing -0.5, 0)}

for (I in 1:length(PerCorrection)){
  GGPLOT=ggplot((StockIData %>% filter(MinCorrection  ==PerCorrection[I])), aes(x = Impulse , y = Correction )) + geom_hex(show.legend=FALSE ) +  xlim(xLim) + ylim(yLim)+labs(x=PerCorrection[I]) +
    theme(axis.title.x = element_text(vjust = 2)) + geom_hline(yintercept=-CriticalSwing, linetype="dashed", color = "red",size=0.5)+ geom_vline(xintercept=CriticalSwing, linetype="dashed", color = "red",size=0.5)
  Name=paste0(Ticker,"_",I)
  assign(Name,ggplotly(GGPLOT))
}
}




    
```



These plots show the mimimum price correction at given price extensions... this is like the zig-zag indicator in trdingview, ploting the increases and decreases of certain sizes.

$$\\[.0005in]$$



# AUDCAD


```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(AUDCAD_1,AUDCAD_2,AUDCAD_3,AUDCAD_4,AUDCAD_5,AUDCAD_6, titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$  

# AUDCHF


```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(AUDCHF_1,AUDCHF_2,AUDCHF_3,AUDCHF_4,AUDCHF_5,AUDCHF_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$  


# AUDJPY


```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(AUDJPY_1,AUDJPY_2,AUDJPY_3,AUDJPY_4,AUDJPY_5,AUDJPY_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$  

# AUDNZD


```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(AUDNZD_1,AUDNZD_2,AUDNZD_3,AUDNZD_4,AUDNZD_5,AUDNZD_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$  


# AUDUSD


```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(AUDUSD_1,AUDUSD_2,AUDUSD_3,AUDUSD_4,AUDUSD_5,AUDUSD_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# CADCHF


```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(CADCHF_1,CADCHF_2,CADCHF_3,CADCHF_4,CADCHF_5,CADCHF_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

$$\\[.0009in]$$    


# CADJPY


```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(CADJPY_1,CADJPY_2,CADJPY_3,CADJPY_4,CADJPY_5,CADJPY_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$  


# CHFJPY


```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(CHFJPY_1,CHFJPY_2,CHFJPY_3,CHFJPY_4,CHFJPY_5,CHFJPY_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$  


# EURAUD 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(EURAUD_1,EURAUD_2,EURAUD_3,EURAUD_4,EURAUD_5,EURAUD_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# EURCAD 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(EURCAD_1,EURCAD_2,EURCAD_3,EURCAD_4,EURCAD_5,EURCAD_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# EURCHF 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(EURCHF_1,EURCHF_2,EURCHF_3,EURCHF_4,EURCHF_5,EURCHF_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# EURGBP 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(EURGBP_1,EURGBP_2,EURGBP_3,EURGBP_4,EURGBP_5,EURGBP_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# EURJPY 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(EURJPY_1,EURJPY_2,EURJPY_3,EURJPY_4,EURJPY_5,EURJPY_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# EURNZD 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(EURNZD_1,EURNZD_2,EURNZD_3,EURNZD_4,EURNZD_5,EURNZD_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# EURUSD 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(EURUSD_1,EURUSD_2,EURUSD_3,EURUSD_4,EURUSD_5,EURUSD_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# GBPAUD 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(GBPAUD_1,GBPAUD_2,GBPAUD_3,GBPAUD_4,GBPAUD_5,GBPAUD_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# GBPCAD 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(GBPCAD_1,GBPCAD_2,GBPCAD_3,GBPCAD_4,GBPCAD_5,GBPCAD_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```


$$\\[.0009in]$$    


# GBPCHF 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(GBPCHF_1,GBPCHF_2,GBPCHF_3,GBPCHF_4,GBPCHF_5,GBPCHF_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# GBPJPY 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(GBPJPY_1,GBPJPY_2,GBPJPY_3,GBPJPY_4,GBPJPY_5,GBPJPY_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# GBPNZD 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(GBPNZD_1,GBPNZD_2,GBPNZD_3,GBPNZD_4,GBPNZD_5,GBPNZD_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# GBPUSD 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(GBPUSD_1,GBPUSD_2,GBPUSD_3,GBPUSD_4,GBPUSD_5,GBPUSD_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# NZDCAD 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(NZDCAD_1,NZDCAD_2,NZDCAD_3,NZDCAD_4,NZDCAD_5,NZDCAD_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$  

# NZDCHF 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(NZDCHF_1,NZDCHF_2,NZDCHF_3,NZDCHF_4,NZDCHF_5,NZDCHF_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

        
$$\\[.0009in]$$  

# NZDJPY 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(NZDJPY_1,NZDJPY_2,NZDJPY_3,NZDJPY_4,NZDJPY_5,NZDJPY_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```


$$\\[.0009in]$$  

# NZDUSD 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(NZDUSD_1,NZDUSD_2,NZDUSD_3,NZDUSD_4,NZDUSD_5,NZDUSD_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# USDCAD 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(USDCAD_1,USDCAD_2,USDCAD_3,USDCAD_4,USDCAD_5,USDCAD_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# USDCHF 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(USDCHF_1,USDCHF_2,USDCHF_3,USDCHF_4,USDCHF_5,USDCHF_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# USDJPY 

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(USDJPY_1,USDJPY_2,USDJPY_3,USDJPY_4,USDJPY_5,USDJPY_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    


# XAUUSD

```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =12, fig.height = 3}
subplot(XAUUSD_1,XAUUSD_2,XAUUSD_3,XAUUSD_4,XAUUSD_5,XAUUSD_6,titleY = FALSE,   titleX = TRUE, margin = 0.015,nrows =1)
```

    
$$\\[.0009in]$$    



[AUDCAD](https://camilo-mora.github.io/OptiMoraR/SwingsNews_AUDCAD.html) 
[AUDCHF](https://camilo-mora.github.io/OptiMoraR/SwingsNews_AUDCHF.html)
[AUDJPY](https://camilo-mora.github.io/OptiMoraR/SwingsNews_AUDJPY.html)
[AUDNZD](https://camilo-mora.github.io/OptiMoraR/SwingsNews_AUDNZD.html) 
[AUDUSD](https://camilo-mora.github.io/OptiMoraR/SwingsNews_AUDUSD.html) 
[CADJPY](https://camilo-mora.github.io/OptiMoraR/SwingsNews_CADJPY.html) 
[CADCHF](https://camilo-mora.github.io/OptiMoraR/SwingsNews_CADCHF.html) 
[CHFJPY](https://camilo-mora.github.io/OptiMoraR/SwingsNews_CHFJPY.html) 
[EURAUD](https://camilo-mora.github.io/OptiMoraR/SwingsNews_EURAUD.html) 
[EURCAD](https://camilo-mora.github.io/OptiMoraR/SwingsNews_EURCAD.html) 
[EURCHF](https://camilo-mora.github.io/OptiMoraR/SwingsNews_EURCHF.html) 
[EURGBP](https://camilo-mora.github.io/OptiMoraR/SwingsNews_EURGBP.html) 
[EURJPY](https://camilo-mora.github.io/OptiMoraR/SwingsNews_EURJPY.html) 
[EURNZD](https://camilo-mora.github.io/OptiMoraR/SwingsNews_EURNZD.html) 
[EURUSD](https://camilo-mora.github.io/OptiMoraR/SwingsNews_EURUSD.html) 
[GBPAUD](https://camilo-mora.github.io/OptiMoraR/SwingsNews_GBPAUD.html) 
[GBPCAD](https://camilo-mora.github.io/OptiMoraR/SwingsNews_GBPCAD.html) 
[GBPCHF](https://camilo-mora.github.io/OptiMoraR/SwingsNews_GBPCHF.html) 
[GBPJPY](https://camilo-mora.github.io/OptiMoraR/SwingsNews_GBPJPY.html) 
[GBPNZD](https://camilo-mora.github.io/OptiMoraR/SwingsNews_GBPNZD.html) 
[GBPUSD](https://camilo-mora.github.io/OptiMoraR/SwingsNews_GBPUSD.html) 
[NZDCAD](https://camilo-mora.github.io/OptiMoraR/SwingsNews_NZDCAD.html) 
[NZDCHF](https://camilo-mora.github.io/OptiMoraR/SwingsNews_NZDCHF.html) 
[NZDJPY](https://camilo-mora.github.io/OptiMoraR/SwingsNews_NZDJPY.html) 
[NZDUSD](https://camilo-mora.github.io/OptiMoraR/SwingsNews_NZDUSD.html) 
[USDCAD](https://camilo-mora.github.io/OptiMoraR/SwingsNews_USDCAD.html) 
[USDCHF](https://camilo-mora.github.io/OptiMoraR/SwingsNews_USDCHF.html) 
[USDJPY](https://camilo-mora.github.io/OptiMoraR/SwingsNews_USDJPY.html) 
[XAUUSD](https://camilo-mora.github.io/OptiMoraR/SwingsNews_XAUUSD.html) 
[ALL](https://camilo-mora.github.io/OptiMoraR/SwingsByALLPairs.html) 
