
---
title: "Ranking of optimized robots"
output: html_document
---

Version: 1.0

```{r, echo=FALSE, message=FALSE,warning=FALSE}
##This code takes files from the optimoraR optimization and rank them by best results.

library(gsheet)
library(dplyr)
library(ggplot2)
library(plotly)

MinimumDD=6000 #Minimun drowdpdown allowed
# reading the sheet data
Data <-gsheet2tbl(  "https://docs.google.com/spreadsheets/d/1F68BJU65ygqCHldMSVrbu82b4_WTIUN8go4jdopu21E/edit?usp=sharing")

GoodOptimizations=Data %>%  filter(MaxDD  < MinimumDD)

BestBot= GoodOptimizations %>%  group_by(Pair) %>% top_n(1, NetProfit) #top Bot by profit within desire DD

BestBot=BestBot[order(BestBot$NetProfit , decreasing = TRUE), ] 


BestBot=BestBot %>% mutate_if(is.numeric, round, digits=1)

BestBot$Rank=paste(sprintf("%02d", 1:nrow(BestBot)),BestBot$Pair)

#do bar plot
Opti=ggplot(BestBot, aes(x=Rank, y=NetProfit ,  fill = NameBot)) +
  geom_col(position = position_dodge())+
  theme_gray()+ 
  theme(legend.title = element_blank(), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

Plot= ggplotly(Opti, tooltip = c( "Rank", "NetProfit"))


Yield=round(sum(BestBot$NetProfit)    ,0)
ExtremeDD=round(sum(BestBot$MaxDD) ,0)   
```

$$\\[.0005in]$$
 <font size="25"> **$`r format(Yield, scientific=FALSE)`  total profit** </font>     
 
 </br>
 
 <font size="10"> **$ `r format( ExtremeDD, scientific=FALSE)` cummulative dropdown** </font>


$$\\[.0005in]$$

Bots are optimized in R by having the largest number of successful entries while meeting as criteria that DD does not exceed the desired DD ($ `r MinimumDD`) and the entry capital is not larger than 10% nor smaller than $1,000 (The smallest amount possible).


Optimized with $30,000 capital, 10% of capital per entry and 10% desired DD.

Those results are then passed by TV and the best Bot for each pair is shown here.


$$\\[.0005in]$$




# Bots per pair


```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.align = 'center', fig.width =9}
Plot

```

    
  

<details>
  <summary>Parameters</summary>
```{r, echo=FALSE, eval=TRUE}
BestBot=BestBot[,c("Pair", "NameBot",   "Configuration",    "NetProfit", "MaxDD")]
knitr::kable(BestBot)
```
</details> 




